The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-31 dit-paper_ieee.tex
feasibility conditions
Final touches (hopefully)

	Abstract models for real-time systems often require the determination of the
	(worst-case) execution time of a job (WCET), a value highly dependent on the
	platform on which the application is deployed.

	Feasibility conditions...

	The \emph{C-space} of a real-time system is, intuitively,
	the set of WCET values for which this system would be feasible. A
	precise and efficient description of its C-space would allow to quickly decide
	whether or not a system is feasible on a given platform.

@@

			As shown in Fig. \ref{fig:asyncBehavior}, the system begins in the
			\emph{incomplete period}, where all tasks are not in the system. Then, after
			$O_{max}$ time units, every tasks is in the system and the \emph{transient
			period} begins. Then, after $O_{max} + H$ time units, the system is faced
			with the same pattern of arrival as in $O_{max}$. However, because in
			$O_{max} + H$ every task is in the system and in $O_{max}$ some were missing,
			the state of the system will be different. The \emph{stationary period} then
			begins. At instant $O_{max} + 2H$ it is guaranteed that the system is in the
			exact same situation it was at instant $O_{max} + H$ (however it may be
			possible to find earlier intervals with the same property).

For this reason, as explained in \cite{leung1982complexity}, it is sufficient to check for intervals included in the interval $[O_{max}, O_{max} + 2H]$, which has an exponential length in the number of tasks.

@@

The FPDIT, if it exists, must occur in the transitive period. Indeed, it cannot occur in the incomplete period by definition ($t_d > O_{max}$) and if it occurred in the $k^{th}$ stationary period, another DIT should have occurred in the transitive period at instant $t_d - k H$ (a contradiction).

As the FPDIT happens when all tasks are in the system, we know that the system will arrive in the exact same state one hyperperiod later ($t_d + H$). We can thus restrict the DBF test to intervals included in the interval $[t_d, t_d + H]$, if the FPDIT exists. This will always be a better interval than $[O_{max}, O_{max} + 2H]$ and if the first periodic DIT does not exist (which can be verified as explained in Section \ref{sct:FPDITexist}), the latter interval can be used.

@@

	\begin{figure}[h]
		\begin{center}
			\includegraphics[width=0.5\textwidth]{figs/sizeRatio.png}
			\caption{C-space size ratio between asynchronous and equivalent synchronous
			systems}
			\label{fig:sizeRatio}
		\end{center}
	\end{figure}

>>>>

	Abstract models for real-time systems often require the determination of the
	worst-case execution time of a job (WCET), a value highly dependent on the
	platform on which the application is deployed. Feasibility conditions allow to
	decide whether a system can be scheduled correctly (i.e. without violating any
	timeliness constraint) based on task parameters, including the WCET.

	The \emph{C-space} of a real-time system is, intuitively,
	the set of WCET values for which this system would be feasible. A
	precise and efficient description of the C-space of a system would allow to quickly decide
	whether or not it is feasible on a given platform.

@@

			As shown in Fig. \ref{fig:asyncBehavior}, the system begins in the
			\emph{incomplete period}, where all tasks are not in the system. Then, after
			$O_{max}$ time units, every tasks is in the system and the \emph{transient
			period} begins. Then, after $O_{max} + H$ time units, the system is faced
			with the same pattern of arrival as in $O_{max}$. However, because in
			$O_{max} + H$ every task is in the system and in $O_{max}$ some were missing,
			the state of the system will be different. The \emph{stationary period} then
			begins. At instant $O_{max} + 2H$ it is guaranteed that the system is in the
			exact same situation it was at instant $O_{max} + H$.

			For this reason, as shown by \cite{leung1982complexity}, it is sufficient (but pessimistic) to
			check for
			intervals included in the interval $[O_{max}, O_{max} + 2H]$, which has an exponential length
			in the number of tasks. A better interval is given in \cite{choquet2004minimal} using the
			notion of cyclic idle times (denoted $t_c$), which are dependent of the execution
			time and therefore cannot be used directly. The interval is $[0, t_c + H]$ and is valid for
			every $t_c$.

			In the following section, we extend the latter interval using the previously defined notion
			of periodic DIT, a particular case of cyclic idle times which does not depend on the execution
			times.

@@

The FPDIT, if it exists, must occur in the transient period. Indeed, it cannot occur in the incomplete period by definition ($t_d > O_{max}$) and if it occurred in the $k^{th}$ stationary period, another DIT should have occurred in the transient period at instant $t_d - k H$ (a contradiction).

As the FPDIT happens when all tasks are in the system, we know that the system will arrive in the exact same state one hyperperiod later ($t_d + H$) (A rigorous proof is given in \cite{choquet2004minimal} for any cyclic idle time). We can thus restrict the DBF test to intervals included in the interval $[t_d, t_d + H]$ if the FPDIT exists. This will always be a better interval than $[O_{max}, O_{max} + 2H]$ and if the first periodic DIT does not exist (which can be verified as explained in Section \ref{sct:FPDITexist}), the latter interval can be used.

@@

	\begin{figure}[h]
		\begin{center}
			\includegraphics[width=0.5\textwidth]{figs/sizeratio.png}
			\caption{C-space size ratio between asynchronous and equivalent synchronous
			systems}
			\label{fig:sizeRatio}
		\end{center}
	\end{figure}
